%% -*- Mode: LaTeX -*- 
%%
%% application-logging.tex
%% Created Fri Jul  1 11:07:46 AKDT 2016
%% by Raymond E. Marcil <rmarcil@gci.com>
%%
%% Application Logging
%%

%% ================== Application Logging ======================
%% ================== Application Logging ======================
\subsubsection{Application Logging}
The filexfer applications log to the \texttt{/var/log/filexfer}
directory on \texttt{prod-prov4-cdr1.}\textbackslash\\
\texttt{operations.gci.com}. The parent \texttt{filexfer} jobs
log to \texttt{filexfer-get.log} and
\texttt{filexfer-}\textbackslash\\
\texttt{put.log}.
The \texttt{jobmonitor} and \texttt{dataloader} applications
log to \texttt{jobmonitor.log} and\\
\texttt{dataloader.log}, The \texttt{filexfer} applications
log to the \texttt{/var/log/filexfer} directory on
\texttt{prod-prov4-cdr1.operations.gci.com}. The parent
\texttt{filexfer} jobs
log to \texttt{filexfer-get.}\textbackslash\\
\texttt{log} and \texttt{filexfer-put.log}. The
\texttt{jobmonitor} and \texttt{dataloader} applications log to\\
\texttt{jobmonitor.log} and \texttt{dataloader.log}, respectively. Each file
transfer job is executed as a child process and gets its own log file. The
format is\\
\texttt{filexfer-}$\{$\texttt{neName}$\}$\texttt{-}$\{$\texttt{idJob}$\}$\texttt{-}$\{$\texttt{get,put}$\}$\texttt{.log}.\\
\\
By default, the jobs log at the warn level.  Adjust the level to info to get a
high-level view of the application's state.  Adjust log verbosity by modifying
the appropriate config file in \texttt{/etc/filexfer}.  The changes will take
effect after the next program execution.\\
\\
Errors are also logged to a database table which can be browsed in the
filexfer web interface under the '\texttt{Logs \& Errors}' view.  This view
includes messages logged at \texttt{warn}, \texttt{error}, and \texttt{fatal}
severity.\footnote{\href{http://oss-wiki.operations.gci.com/dev/index.php/Usage\_Collection\_Framework\_(filexfer)}{Usage Collection Framework (filexfer)}}

